---
title: "Intalling Packages for Predictive Analytics"
author: "Francois Collin"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  BiocStyle::html_document:
    toc: true
    # does this have an effect
    fig_caption: yes    
    # this has no effect
    number_sections: yes
bibliography: ../../bibFiles/bibFile.bib
#csl: ../acm-sig-proceedings.csl  - doest work with pandoc-siteproc
csl: ../../bibFiles/cell-numeric.csl
#biblio-style: acm
link-citations: true
vignette: >
 %\VignetteEncoding{UTF-8}
---

<style type="text/css">

body{ /* Normal  */ 
 font-size: 14px; 
}
td {  /* Table  */ 
 font-size: 12; 
}
h1.title { 
 font-size: 28px; color: DarkGreen; 
}
h1 { /* Header 1 */ 
 font-size: 24px; color: DarkBlue; 
}
h2 { /* Header 2 */ 
 font-size: 18px; color: DarkBlue; 
}
h3 { /* Header 3 */ 
 font-size: 18px;
 font-family: "Times New Roman", Times, serif;
 color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

```{r GlobalOptions, results="hide", include=FALSE, cache=FALSE}
knitr::opts_knit$set(stop_on_error = 2L) #really make it stop
#knitr::dep_auto()
```


```{r Prelims, include=F, echo=FALSE, results='hide', message=FALSE} 

 FN <- "M0A-installPackages"

  suppressMessages(require(rmarkdown))
  suppressMessages(require(knitr))
  options(stringsAsFactors=F) 

  # Shotcuts for knitting and redering while in R session
  kk <- function(n='') knit2html(paste("Scripts/t", n, sep=''), envir=globalenv(),
        output=paste('Scripts/',FN,".html", sep=''))

  rr <- function(n='') render(paste("Scripts/t", n, sep=''), envir=globalenv(),
        output_file=paste(FN,".html", sep=''), output_dir='Scripts')

  bb <- function(n='') browseURL(paste('Scripts/',FN,".html", sep=''))

  # The usual shorcuts
  zz <- function(n='') source(paste("Scripts/t", n, sep=''))

  if(file.exists('/Users/francois/Dropbox/PredictiveModeling/CC/R/'))
  WRKDIR <- '/Users/francois/Dropbox/PredictiveModeling/CC/R/'  else
  WRKDIR <- '/mnt100/home/Dropbox/PredictiveModeling/CC/R'

  if(!file.exists(WRKDIR)) stop("WRKDIR ERROR", WRKDIR)

  # do once
  #setwd(WRKDIR)

  # file rmarkdown file management options: cache, figures
  #cache_DIR <- file.path(WRKDIR, 'Scripts', 'cache/M0A/')
  #suppressMessages(dir.create(cache_DIR, recursive=T))
  #opts_chunk$set(cache.path=cache_DIR)

  #figure_DIR <- file.path(WRKDIR, 'Scripts', 'figure/M0A/')
  #suppressMessages(dir.create(figure_DIR, recursive=T))
  #opts_chunk$set(fig.path=figure_DIR)

```

```{r runParam, echo=F}
 INSTALL <- T
```

***
# Install R Packages {#Install}

## Packages for Predictive Analytics {#InstPred}


* Example citation: 
This strategy draws ideas from the "tight clustering" algorithm used to find groups of genes in microarray data in [@tseng2005].

```{r SDDS, eval=F, echo=F}

 ### SDDA had to be fetched from archives
 install.packages('SDDA_1.0-5.tar.gz')

```
<!-- ***************************************************** -->

```{r installPredictive, eval=T}

 #cat("Installing caret and dependencies\n")
 #if(INSTALL) install.packages("caret", dependencies = c("Depends", "Suggests"))

 RequiredPkgs.vec <- 
  c('GEOquery', 'hgu133plus2.db',
    'caret', "gpls", "logicFS", "vbmp",'pROC','pamr','randomForest',
    'kernlab', 'gbm', 'xgboost', 'SDDA')

 InstalledPkgs.vec <- installed.packages()[,1]
 ToInstall.vec <- setdiff(RequiredPkgs.vec,InstalledPkgs.vec)

 cat("Pkgs to install:", ifelse(length(ToInstall.vec),ToInstall.vec,'None'), '\n')

 if(INSTALL & length(ToInstall.vec)){
  source("http://www.bioconductor.org/biocLite.R")
  biocLite(ToInstall.vec, dependencies=F)
 }

```

## Check Installed Packages

```{r checkInstall}

 for(PKG in ToInstall.vec){
  cat("Checking", PKG, '\n')
  tryCatch(library(PKG))
 }

```

<!-- Put bib here If applicable 
-->
# References
<div id="refs"></div>

***
# Parameter settings
  * WRKDIR = `r WRKDIR`
  * FN = `r FN`
  * Scripts = Scripts
  * RUN DATE = `r date()`
  * INSTALL = `r INSTALL`

```{r, echo=F}
 sessionInfo()
```


```{r, echo=F}
  knit_exit()
```

### ARCHIVAL CODE BELOW

``` 
[R blog](https://www.r-bloggers.com/how-to-install-r-on-linux-ubuntu-16-04-xenial-xerus/)
 sudo echo "deb http://cran.rstudio.com/bin/linux/ubuntu trusty/" | sudo tee -a /etc/apt/sources.list

 gpg --keyserver keyserver.ubuntu.com --recv-key E084DAB9

 gpg -a --export E084DAB9 | sudo apt-key add -

 sudo apt-get update
 sudo apt-get install r-base r-base-dev

...
```

### Update R

[updateR](https://andreacirilloblog.wordpress.com/2015/10/22/updater-package-update-r-version-with-a-function-on-mac-osx/)

```{r updateR, eval=F}
  # DO ONCE
  require(devtools)
  install_github('andreacirilloac/updateR')
 
  suppressMessages(require(updateR))

  updateR(admin_password = "***os_admin_user_password***")
  #### Everything went smoothly, R was updated to R version 3.4.0 (2017-04-21) -- "You Stupid Darkness"

```


### Upgrade bioconductor

```{r upgradeBioc, eval=F}
  source("http://www.bioconductor.org/biocLite.R")
  biocLite("BiocUpgrade")

  # check versions
  #### Error: Bioconductor version 3.5 can be upgraded, but only to 'devel'; see ?useDevel.

```
<!-- ***************************************************** -->



```{r installGithub, echo=F, eval=F}
 require(devtools)
 install_github("RS3","Gastrograph")

```

```
 ### This doesn't work!
 ### Dynamic rmarkdown requires shiny app!!!

 cat("Pkgs to install:", ToIntall.vec, '\n')
 CONTINUE <- F
 while(!CONTINUE) {
  cat("Continue? (Yes/No): ")
  Ans <- scan("stdin", what='',  n=1, quiet = TRUE) 
  if(Ans=='No') q('no')
  if(Ans=='Yes') CONTINUE <- T
 }

<!-- To run
sudo nohup Rscript -e "knitr::knit2html('M0A-installPackages.Rmd')" > M0A-installPackages.log  &

# Or
sudo nohup Rscript -e "rmarkdown::render('M0A-installPackages.Rmd')" > M0A-installPackages.log  &

-->

